### 2014-10-18 fundamentals/intro.tex
cleanup

The architecture within the \Cyclus tool allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This `encapsulated,' `plug-in'
design choice achieves two things. First, analysts across 
research institutions can take advantage of the simulation logic \gls{API} and 
archetype ecosystem when they apply \Cyclus to their specific problem. This 
extensibility, magnified by an open source development process, frees the 
community of users to contribute desired features independen from the team of 
\Cyclus core developers. This mend-and-extend 
paradigm, common in modern software development, reduces maintenance overhead 
and improves code robustness \cite{citation_needed}. Finally, the researcher 
can therefore focus on creating or customizing 
nuclear facility, institution, resource, and toolkit models within their 
specific area of technical expertise.

@@

\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it takes advantage of modern computing resources.  
Furthermore, agent-based modeling provides an analyst a more natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context for example, an analyst can design an agent with reactor-related logic 
and a separate agent with fuel fabrication-related logic. In the \Cyclus 
agent-based context, defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bonafide actors in the simulation. The two archetype libraries, therefore, need 
not have any shared knowledge of one another for them to be building blocks in 
the same simulation.

System dynamics popular approach for modeling nuclear fuel cycles in current
tools \cite{VISION,CAFCA}. It has been shown in the literature
\cite{macal_agent-based_2010} that any system dynamics model can be translated
into an agent-based model. Furthermore, it has been shown that agent-based
techniques can provide a richer model than can system dynamics. Formally, the
set of system dynamics models is a strict subset of agent-based models.

@@

This generality specifically permits the use cases that cannot be achieved with 
fleet-based models. That is, some questions require resolution at the level of 
individual facilities and individual materials.  Since fleet-based, 
lumped-material models do not distinguish between discrete facility entities or 
discrete materials, many detailed performance metrics cannot be captured with 
those tools.

>>>>

The architecture within the \Cyclus tool allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This `encapsulated,' `plug-in'
design choice achieves two things.

First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features independen from the team of \Cyclus core developers. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness \cite{citation_needed}. 
Finally, the researcher can therefore focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise.

@@

\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it takes advantage of modern computing resources.  
Furthermore, agent-based modeling provides an analyst a more natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context for example, an analyst can design an agent with reactor-related logic 
and a separate agent with fuel fabrication-related logic. 
 Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bonafide actors in the simulation.  The two archetype libraries, therefore, need 
not have any shared knowledge of one another for them to be building blocks in 
the same simulation.

System dynamics is a popular approach for modeling nuclear fuel cycles in current
tools \cite{VISION,CAFCA}. However, it has been shown in systems analysis literature
\cite{macal_agent-based_2010} that, formally, the
set of system dynamics models is a strict subset of agent-based models.
That is, any system dynamics model can be translated
into an agent-based model. Furthermore, agent-based
techniques can provide a richer model than can system dynamics. To enable the 
broadest range of simulations in a generic fashion, \gls{ABM} is therefore 
superior to system dynamics.

@@

This generality specifically permits many use cases that cannot be achieved with 
fleet-based models. That is, some questions require resolution at the level of 
individual facilities and individual materials.  Since fleet-based, 
lumped-material models do not distinguish between discrete facility entities or 
discrete materials, many detailed performance metrics cannot be captured with 
those tools.
